Supplement

### 2022-07-18 analysis/article.Rmd
feat: generate png and pdfs for each plot

```{r flowchart, results = "asis", eval = knitr::is_html_output(), echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "Flowchart Inclusion/Exclusion."}
graph <- "
digraph flowchart {
    graph [splines = false];

@@

```{r bootrcv, echo = FALSE, fig.width = 8, fig.height = 6, fig.cap = paste('Calibration of AMELD in comparison to MELD, MELD-Na and MELD-Plus7.\n The points mark the mean predicted survival of', ameldcfg$m, 'patients per interval against their observed mean survival. The error bars correspond to the 95 % confidence interval of the survival estimate.'), echo = FALSE}
par(cex = 0.9)
plot(
    bootrcv,
    what = "calibration",
    main = "90-day survival",
    legend = FALSE
)

>>>>

```{r flowchart, results = "asis", eval = knitr::is_html_output(), echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "Flowchart Inclusion/Exclusion.", dev = c("png", "pdf")}
graph <- "
digraph flowchart {
    graph [splines = false];

@@

```{r bootrcv, echo = FALSE, fig.width = 8, fig.height = 6, fig.cap = paste('Calibration of AMELD in comparison to MELD, MELD-Na and MELD-Plus7.\n The points mark the mean predicted survival of', ameldcfg$m, 'patients per interval against their observed mean survival. The error bars correspond to the 95 % confidence interval of the survival estimate.'), dev = c('png', 'pdf'), echo = FALSE}
par(cex = 0.9)
plot(
    bootrcv,
    what = "calibration",
    main = "90-day survival",
    legend = FALSE
)

### 2022-07-18 analysis/supplement.Rmd
feat: generate png and pdfs for each plot

```{r benchmark-plot, fig.cap = "Benchmark results of machine learning algorithms.", echo = FALSE, fig.width = 18, fig.height = 12}
tar_load(bmrk_results)
r <- bmrk_results$clone()
id <- grep("^scale", x = r$learners$learner_id, invert = TRUE, value = TRUE)
r$filter(task_id = "zlog_eldd", learner_id = id)
autoplot(r) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

@@

```{r roc-plot, echo = FALSE, fig.width = 18, fig.height = 12}
tar_load(timeROC_MELD)
tar_load(timeROC_MELDNa)
tar_load(timeROC_MELDPlus7)
tar_load(timeROC_RCV)

@@

```{r vimpbs, fig.width = 8, fig.height = 10, fig.cap = "Variable importance by frequency of bootstrap selections.", echo = FALSE, message = FALSE}
tar_load(bootrcv)
plot(bootrcv, what = "selected", cex = 0.5)
```

```{r vimprf, fig.width = 8, fig.height = 10, fig.cap = "Variable importance by logrank in random forest.", echo = FALSE, message = FALSE}
tar_load(rngr)
plot_dots(
    sort(rngr$variable.importance),
    main = "Variable importance (random forest)",
    xlab = rngr$splitrule
)
```

>>>>

```{r benchmark-plot, fig.cap = "Benchmark results of machine learning algorithms.", echo = FALSE, fig.width = 18, fig.height = 12, dev = c("png", "pdf")}
tar_load(bmrk_results)
r <- bmrk_results$clone()
id <- grep("^scale", x = r$learners$learner_id, invert = TRUE, value = TRUE)
r$filter(task_id = "zlog_eldd", learner_id = id)
autoplot(r) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

@@

```{r roc-plot, echo = FALSE, fig.width = 18, fig.height = 12, dev = c("png", "pdf")}
tar_load(timeROC_MELD)
tar_load(timeROC_MELDNa)
tar_load(timeROC_MELDPlus7)
tar_load(timeROC_RCV)

@@

```{r vimpbs, fig.width = 8, fig.height = 10, fig.cap = "Variable importance by frequency of bootstrap selections.", dev = c("png", "pdf"), echo = FALSE, message = FALSE}
tar_load(bootrcv)
plot(bootrcv, what = "selected", cex = 0.5)
```

```{r vimprf, fig.width = 8, fig.height = 10, fig.cap = "Variable importance by logrank in random forest.", dev = c("png", "pdf"), echo = FALSE, message = FALSE}
tar_load(rngr)
plot_dots(
    sort(rngr$variable.importance),
    main = "Variable importance (random forest)",
    xlab = rngr$splitrule
)
```
